### 2021-11-30 text/outline/draft.tex
update passing of workdir to nextflow script in Gasperini data analysis
update Xie qc to make it more similar to gasperini

\begin{document}
\noindent
Tim, Gene, Kathryn
\begin{center} 
\textbf{A class of exponential family measurement error models, with application to single-cell CRISPR screens}
\end{center}

@@

\section{Generalized linear model with errors in variables}

@@

>>>>

\begin{document}
\noindent
Tim, Gene, Kathryn
\begin{center} 
\textbf{A class of exponential family measurement error models applied to single-cell CRISPR screens}
\end{center}

@@

\section{GLM-based errors-in-variables}

@@

\section{Real data analysis details}

We performed quality control. We kept cells with percent mitochondrial reads less than 8$\%$. For the Gasperini dataset, we furthermore kept cells with UMI and gRNA counts in the 5th to 95th percentiles to reduce the effect of outliers. (We did not perform this latter filter on the Xie data, as the latter dataset appeared to be less noisy and contained fewer cells.) Next, we kept genes expressed in at least $10\%$ of cells with a mean expression level of at least $1$. We did not QC the gRNAs.

The quality-controlled Xie dataset contained $n = 101,508$ cells, $1,030$ genes, and $516$ gRNAs. There were $50,000$ \textit{in silico} negative control pairs and $681$ candidate \textit{cis} pairs. The quality-controlled Gasperini dataset contained $n = 170,645$ cells, $2,079$ genes, $6,598$ gRNAs. There were $17,028$ candidate \textit{cis} pairs, $97,818$ negative control pairs, and $322$ positive control pairs.
